Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm. However, since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be guaranteed. Nevertheless, the proposed framework is more stable than using EKS as the E-step due to better performance of the URTSS.
\begin{itemize}
	\item itterative EM and correlation analysis (maybe)
	\item{comment on EM might convrge to suboptimal solution,simulated
annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
\end{itemize}

>>>>

While EKS has been  applied in the context of EM algorithm for learning a nonlinear model from data \cite{Ghahramani1999} this is the first work (to the best authors' knowlege) where the URTSS has been used to perform state inference in the E-step of the EM algorithm. However, as in the case of EKS since an approximate lower bound is maximised at each time step there is no guarantee that URTSS increases the lower bound on the true likelihood function and therefore the stability of the algorithm cannot be ensured. Nevertheless, the proposed framework is more stable due to better performance of the URTSS.
\begin{itemize}
	\item itterative EM and correlation analysis (maybe)
	\item{comment on EM might convrge to suboptimal solution,simulated
annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
\end{itemize}
